---
title: "Final Project"
author: "Delaney Heileman"
date: "4/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(car)
library(leaps)
library(lubridate)
library(rvest)
library(olsrr)
library(corrplot)
library(leaps)
library(tidyverse)
library(ggplot2)
source("http://www.reuningscherer.net/s&ds230/Rfuncs/regJDRS.txt")

```

## Loading Data 

```{r}
#Setting working directory 
setwd("/Users/delaneyheileman/Documents/school/Yale/Spring 2022/data/ENV757")
#setwd("/Users/liamgunn/Documents/School/Yale Forestry/Spring 2022/Data Exploration & Analysis/Data Analysis Final Project/ENV757")
#setwd("/Users/elain/Documents/GitHub/ENV757")

#Loading CSV 
recs <- read.csv("recs2015_public_v4.csv")
#Gettign dimensions of our dataset 
dim(recs)
#Printing first 6 lines 
head(recs)

#Selecting columns we care about 
recs1 <- na.omit(recs[, c("MONEYPY", "ENERGYASST", "REGIONC", "DIVISION","UATYP10", "KOWNRENT", "THERMAIN", "PROTHERM", "TEMPHOME", "AIRCOND","CENACHP", "THERMAINAC", "PROTHERMAC", "TEMPHOMEAC", "HOUSEHOLDER_RACE", "SCALEB", "KWH", "DOLLAREL", "DOLLARNG", "DOLLARLP", "DOLLARFO")])

#Removing "not applicable" answers for thermostat questions. N/a for Thermostat likely means they use wood fire or something else
cleanRECS <- recs1[recs1$THERMAIN != -2 & recs1$THERMAINAC != "-2",]

cleanRECS$REGIONC <- as.factor(recode(cleanRECS$REGIONC,
                             '1' = 'Northeast',
                             '2' = 'Midwest',
                             '3' = 'South',
                             '4' = 'West'))

#Changing C (suburban areas) into Urban
cleanRECS$UATYP10 <- recode(cleanRECS$UATYP10, 'C' = 'U')



cleanRECS$DIVISION <- as.factor(recode(cleanRECS$DIVISION,
                              '1' = 'New England',
                              '2' = 'Mid Atlantic',
                              '3' = 'East North Central',
                              '4' = 'West North Central',
                              '5' = 'South Atlantic',
                              '6' = 'East South Central',
                              '7' = 'West South Central',
                              '8' = 'Mountain North',
                              '9' = 'Mountain South',
                              '10'= 'Pacific'))

#Why are we doing this? Not obvious
cleanRECS$HOUSEHOLDER_RACE <- as.factor(recode(cleanRECS$HOUSEHOLDER_RACE,
                                   '7' = '5'))

cleanRECS$HOUSEHOLDER_RACE <- recode(cleanRECS$HOUSEHOLDER_RACE,
                                   '1' = 'White',
                                   '2' = 'Black/Afr.American',
                                   '3' = 'Native American',
                                   '4' = 'Asian',
                                   '5' = 'Other')

cleanRECS$MONEYPY <- recode(cleanRECS$MONEYPY,
                           '1' = '1 - 20k',
                           '2' = '2 - 40k',
                           '3' = '3 - 60k',
                           '4' = '4 - 80k',
                           '5' = '5 - 100k',
                           '6' = '6 - 120k',
                           '7' = '7 - 140k',
                           '8' = '8 - 140k+')


cleanRECS$CENACHP <- recode(cleanRECS$CENACHP,
                            '1' = 'YES',
                            '0' = 'NO')
#recoding energy assitance variable to yes or no value
cleanRECS$ENERGYASST <- recode(cleanRECS$ENERGYASST,
                            '1' = 'YES',
                            '0' = 'NO')
#Why are we doing this? Not obvious
table(recs1$AIRCOND)
table(recs1$THERMAIN)
table(cleanRECS$THERMAINAC)
table(cleanRECS$CENACHP)
table(cleanRECS$PROTHERMAC)
table(cleanRECS$AIRCOND)
```

## DATA AND DATA CLEANING WRITE UP 

blah blah blah 

this is what we used ______ and the units were _____ 

clean was hard for x y and z reason 

```{r}
#boxplot of kilo watt hours based on area 
boxplot(KWH ~ UATYP10 , data = cleanRECS, col = as.factor(cleanRECS$KWH), xlab = "Rural or Urban")

#adding column for log KWH values
cleanRECS$logKWH <- log(cleanRECS$KWH)

#boxploot of log valeus 
boxplot(logKWH ~ UATYP10 , data = cleanRECS, col = as.factor(cleanRECS$logKWH), xlab = "Rural or Urban")

#WHY IS THIS DOING THIS!!!!!!!

#t.test of KWH and region type 
(test1 <- t.test(logKWH ~ UATYP10, data = cleanRECS, conf.level = .95))

##This is where bootstrapping starts! 

set.seed(230)

N <- 10000
sR <- rep(NA, N)
sU <- rep(NA, N)
diffvals <- rep(NA, N)

for (i in 1:N) {
  sR <- sample(cleanRECS$logKWH[cleanRECS$UATYP10 == "R"],
               sum(cleanRECS$UATYP10 == "R"), replace = TRUE)

  sU <- sample(cleanRECS$logKWH[cleanRECS$UATYP10 == "U"],
               sum(cleanRECS$UATYP10 == "U"), replace = TRUE)
diffvals[i] <- mean(log(sR)) - mean(log(sU))

}

ci <- quantile(diffvals, c(0.025, 0.975))
round(ci, 2)

hist(diffvals, 
     col = "blue", 
     main = "Bootstrapped Sample Means Diff in KiloWattHours", 
     xlab = "", 
     breaks = 50, 
     xlim = c(0.03, 1))

#Add lines to histogram for CI's
abline(v = ci, lwd=3, col="red")
abline(v = test1$conf.int, lwd = 3, col = "green", lty = 2)
legend("topleft", 
       c("Original CI","Boot CI"), 
       lwd = 3, 
       col = c("green","red"), 
       lty = c(2,1))

```



##ANCOVA AREA - ELAINE !!!!!!!
```{r}
## ANCOVA - Analysis of Covariance - ELAINE
  
#This r-markdown is for the purposes of analyzing the continuous variables of kilowatt-hours versus annual gross income and race. 

table(cleanRECS$AIRCOND)
ancmod <- cleanRECS[c("KWH", "MONEYPY", "CENACHP", "HOUSEHOLDER_RACE")]


ancmod$MONEYPY <- as.factor(ancmod$MONEYPY)
ancmod$CENACHP <- as.factor(ancmod$CENACHP)
ancmod <- na.omit(ancmod)
dim(ancmod)
str(ancmod)
```

## Exploratory Data Analysis 
```{r}

attach(ancmod)
boxplot(KWH ~ MONEYPY, data = ancmod, col = "green", xlab = "Annual Gross Income")
boxplot(KWH ~ CENACHP, data = ancmod, col = "yellow", xlab = "Thermostat")


dim(ancmod)

```


## Assumption Verification

The following assumptions must be met in order to proceed with an ANCOVA analysis: the dependent variables should be normally distributed, data should have approximately the same variance

```{r}
#Variances


stdev1 <- tapply(KWH, MONEYPY, sd)
round(max(stdev1)/min(stdev1),1)

stdev2 <- tapply(KWH, CENACHP, sd)
max(stdev2)/min(stdev2)

#check assumptions for KWH and MONEYPY
m1 <- lm(KWH ~ MONEYPY, data = ancmod)
#plot(ancmod$KWH ~ ancmod$MONEYPY, data = ancmod, pch = 19, main = "Kilowatt Hours by Gross Annual Income", col = "red")# this isn't working for some reason atm
summary(m1)

#checking normality 
myResPlots2(m1)


trans1 <- boxCox(m1)
trans1$x[which.max(trans1$y)]


#log transformation 
ancmod$logKWH <- log(ancmod$KWH)
ancmod <- ancmod[-4913, ] #why isn't this being removed???

m2 <- lm(logKWH ~ MONEYPY, data = ancmod)
summary(m2)
myResPlots2(m2)

ancmod[3365,]
ancmod[4913,] 

#check assumptions for KWH and CENACHP

m3 <- lm(logKWH ~ CENACHP, data = ancmod)
summary(m3)
myResPlots2(m3)



```


*The residual plots show an unequal spread of points about 0 which indicates multiple outliers or influential points. The normal quantile plot is not straight indicating evidence of heteroskedasticity. The boxcox lambda value is 0.22 which suggests a transformation to the power of a 1/4 or we could round to 0 which would suggest a transformation of log. After transformation, we manage to fix some of the heteroskedasticity. When looking at specific outliers, one of the rows, 4913 has no data attached to it so it will be removed. * 

```{r}
fitanco <- lm(logKWH ~ MONEYPY + CENACHP + MONEYPY*CENACHP, data = ancmod)

Anova(fitanco, type = 3)
summary(fitanco)

anccoef <- coef(fitanco)
plot(logKWH ~ MONEYPY, data = ancmod, col = factor(CENACHP), pch = 16) #why is it boxplots???? 
```



```{r}
##FROM CLASS 19
#Creating the linear model
lm1 <- lm(MEGAWATT_HOURS ~ HOUSEHOLD_INCOME*CLIMATE_REGION, data = x)
coefs <- round(coef(lm1), 2)

#Ploting the model
plot(MEGAWATT_HOURS ~ HOUSEHOLD_INCOME,
     data = x,
     col = factor(CLIMATE_REGION), 
     pch = 16,
     cex = .5)
legend("topleft", col = 1:5, legend = levels(factor(x$CLIMATE_REGION)), pch = 16)

#Plotting the different best fit lines
abline(a = coefs[1], b = coefs[2], col = "black", lwd = 3)
for (i in 3:6){
  abline(a = coefs[1] + coefs[i], b = coefs[2] + coefs[i+4], col = (i-1), lwd = 3)
}
```


