---
title: "Final Project"
author: "Delaney Heileman"
date: "4/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(car)
library(leaps)
library(lubridate)
library(rvest)
library(olsrr)
library(corrplot)
library(leaps)
```

## Loading Data 

```{r}
#Setting working directory 
setwd("/Users/delaneyheileman/Documents/school/Yale/Spring 2022/data/ENV757")

#Loading CSV 
recs <- read.csv("recs2015_public_v4.csv")
dim(recs)
head(recs)

#selecting columns we care about 

#WE NEED TO DECIDE WHAT WE WANT TO DO ABOUT IMPUTATION 
recs1 <- na.omit(recs[, c("MONEYPY", "ENERGYASST", "REGIONC", "DIVISION", "KOWNRENT", "THERMAIN", "PROTHERM", "TEMPHOME", "AIRCOND","CENACHP", "THERMAINAC", "PROTHERMAC", "TEMPHOMEAC")])

#getting rid of "not applicable" answers for thermostat questions. N/a for Thermostat likely means they use wood fire or something else
cleanRECS <- recs1[recs1$THERMAIN != "-2" & recs1$PROTHERM != "-2" & recs1$THERMAINAC != "-2" & recs1$PROTHERMAC != "-2",]

cleanRECS$REGIONC <- as.factor(recode(cleanRECS$REGIONC, 
                              "'1' = 'Northeast';
                               '2' = 'Midwest';
                               '3' = 'South'; 
                               '4' = 'West'"))

cleanRECS$DIVISION <- as.factor(recode(cleanRECS$DIVISION, 
                              "'1' = 'New England';
                               '2' = 'Mid Atlantic';
                               '3' = 'East North Central'; 
                               '4' = 'West North Central';
                               '5' = 'South Atlantic';
                               '6' = 'East South Central';
                               '7' = 'West South Central';
                               '8' = 'Mountain North';
                               '9' = 'Mountain South';
                               '10'= 'Pacific'"))

```


#Columns we care about: 

MONEYPY (Annual income)

ENERGYASST (participated in home energy assitnce program)

REGIONC (region)

DIVISION (census region)

KOWNRENT

THERMAIN (any thermostats)

PROTHERM (programable therm)

TEMPHOME (Temp in winter when someone is home)

AIRCOND(air conditioner used y/n)

CENACHP (heat pump y/n)

THERMAINAC (Thermostat for air conditioner)

PROTHERMAC (programable therm for air coniditoner)

TEMPHOMEAC (summer temp when people are home)

You can also embed plots, for example:

```{r}

boxplot(TEMPHOME$cleanRECS ~ MONEYPY$cleanRECS, col = as.factor(cleanRECS$MONEYPY))

boxplot(TEMPHOMEAC ~ MONEYPY, data = cleanRECS, col = as.factor(cleanRECS$MONEYPY))

boxplot(TEMPHOME ~ REGIONC, data = cleanRECS, col = as.factor(cleanRECS$REGIONC))

boxplot(TEMPHOMEAC ~ REGIONC, data = cleanRECS, col = as.factor(cleanRECS$REGIONC))
```


